---
title: "Assignment_API"
author: "Andreina A"
date: "2024-11-02"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(httr)
library(data.table)
```

## Assignment 9

The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.



**The api data I used from NY times was on books by Stephen King. To obtained the data frame from the json file I used fromJSON function, and the class function to identify the data frame within the json file. To start, I recreated the URL link to hide my API key using the paste0 function and I hide my api key into my environment by creating a variable api_key.**

```{r}
api_key <- Sys.getenv("NYTIMES_API_KEY")
NYT<-"https://api.nytimes.com/svc/books/v3/reviews.json?author=Stephen+King&api-key="
Full<-paste0(NYT,api_key) #paste0 function creates a string from the NYTI and api_key with no spaces in between 
```


```{r}
url<-fromJSON(Full, flatten= TRUE)

Book_Review<-url$results #obtaining data frame from file
class(Book_Review)
```

## Data frame

**Using the data table function to create a table from the data frame.**

```{r}
Book_table<-data.table(Book_Review)
Book_table
```

## Conclusion

**I was able to access and load the api data from New York Times, and create a data frame the json file. By creating a variable into the environment of R I was able to hide my api key, and load the url with my api key hidden. In this assignment I learned how to create api keys and how to use them to load the data into R without having to download the data and upload it into R.**


